%% start of file 'moderncv jordi.tex'.
%% Copyright 2012-2020 Jordi Burgos (jordiburgos@gmail.com).
%


\documentclass[10pt,a4paper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\sfdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                  % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                         % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
%\usepackage[scale=0.79]{geometry}
\usepackage[left=2cm,right=2.5cm,top=3cm,bottom=2.5cm]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}           % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}      % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\firstname{Jordi}
\familyname{Burgos L\'{o}pez}
\title{Senior Software Engineer}               % optional, remove the line if not wanted
%\address{5th Street St}{46200 Somewhere - Spain}    % optional, remove the line if not wanted
%\mobile{+34 000 000 000}                     % optional, remove the line if not wanted
%\phone{+2~(345)~678~901}                      % optional, remove the line if not wanted
%\fax{+3~(456)~789~012}                        % optional, remove the line if not wanted
\email{jordiburgos@gmail.com}                          % optional, remove the line if not wanted
%\homepage{jordiburgos.com}                    % optional, remove the line if not wanted
%\extrainfo{additional information}            % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                  % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                     % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

I am a passionate developer.
Regularly, I enjoy attending conferences and meetups to keep me up to date.
Besides, I like to develop personal projects to improve my knowledge.
I like to work with people, I am nice and easy to work with.
In addition I have experience training and mentoring team members.

\section{Experience}

\cventry{2019--Present}{Lead Software Development Engineer}{Mastercard}{Dublin, Ireland}{}{
Multinational Company; 18.600 employees; Financial Services, Technology.
\begin{itemize}%
    \item \textbf{LLL}: Research and Development for 
    \begin{itemize}%
    	\item Next Edge - 
Next generation of Mastercard’s customer facing “intelligent edge”
A single point of entry for all things Mastercard – consistent onboarding and operational experience across products and services
The only piece of Mastercard that the customer needs to see
“Future proof” – flexibility to add/modify services, and deploy new products at the edge
Modern, service oriented architecture design - “run anywhere” (public/private customer cloud environments, our own cloud implementations)

	\item Event Framework - 
	
As we work to enable building applications that leverage an event driven architecture and also streamline the developer journey for such applications, we endeavor to provide a supporting application framework such that business functionality can be delivered with the simplest, smallest coding effort. The business functionality is currently envisioned to be delivered as a simple jar. To realize this simple development model, the application frameworks, messaging platforms, security services and tools required to deliver, integrate and operate applications will be integrated into an application framework that provides all of the boilerplate code and “plumbing” necessary to achieve required security and operational requirements. We refer to this as the Event Framework.

To achieve this goal we will use standards based frameworks, tools and patterns to ensure the sustainability of the platform.
	
        \item Service design bootstraping (Vulcan + vulcan-cli/Polaris) - Lead, strategy + design
	
Vulcan is a tool to allow developers to quickly set up a new project by choosing the use-cases their application will implement.

The goal of the Paved Path is to enable developers across all teams in Mastercard focus on writing the required business functionality that our customers require, in a consistent way, in accordance with the Engineering Principles. More elaboration about this can be found on this article from Steve Bagby, CTO Enterprise Architecture.


	
    \end{itemize}
\end{itemize}
}


\cventry{2016--2019}{Senior Software Engineer}{SAP}{Dublin, Ireland}{}{
Multinational Company; 85.000 employees; Business Operations and Customer Relations.
\begin{itemize}%
    \item \textbf{SAP Analytics Cloud}: Collect and produce statistics for dataset fields and metadata search. Java, Spring, JMS, REST, SAP HANA SQL.
    \begin{itemize}%
        \item Design and implement service architecture using Spring and JMS.
		\item Design database structure and analysis SQL queries.
		\item Implement service to support several cloud providers.
    \end{itemize}
    \item \textbf{Predictive Analytics}: Software to create Machine Learning and Big Data processing pipelines graphically. Java, JavaScript, TypeScript, Webpack, SAP HANA database, SAP UI5.
    \begin{itemize}%
        \item Design and implement user interface architecture with Webpack and SAP UI5.
		\item Implement application functionality in Typescript.
		\item Train and supervise junior developers in the team.
		\item Investigate and resolve bugs from server side code base.
		\item Identify platform improvements and document them.
    \end{itemize}
\end{itemize}
}

\cventry{2014--2016}{Senior Software Engineer}{IBM}{Dublin, Ireland}{}{
Multinational Company; 400.000 employees; IT consulting.
\begin{itemize}%
    \item \textbf{HR suite project}: Software suite for HR related applications. Java, REST, JPA, JAX-RS, HTML, CSS, JavaScript, AngularJS, IBM WebSphere, Linux.
    \begin{itemize}%
        \item Design and implement architecture of back-end REST services with JAX-RS and JPA on WebSphere servers.
        \item Design and implement AngularJS user interface with connection to the REST back-end.
        \item Investigate and select the best technologies suitable for the project.
        \item Collaborate with User Experience (UX) team on the design of interface.
        \item Work using Agile and Test Driven methodology.
    \end{itemize}
\end{itemize}
}

\cventry{2006--2014}{Java Software Engineer}{GFT IT Consulting, S.L.U.}{Valencia, Spain}{}{
Multinational Company; 4.800 employees; IT and Services industry.
\begin{itemize}%
    \item \textbf{Global Funds Derivatives Tracker}: Capture fund derivatives business at Deutsche Bank. It is a repository of core funds, market data, derivatives, executed trades and documentation. Java, Spring, Hibernate, Oracle PL/SQL, HTML, CSS, JavaScript, AJAX, ExtJS, Linux.
    \begin{itemize}%
        \item Agile methodology using Scrum to build technical solutions for banking applications.
        \item Create reusable components and code to increase developers performance.
        \item Optimize the application at all levels: presentation, communications and database.
        \item Provide technical support to team members.
    \end{itemize}
    \item \textbf{Feed Consolidation Layer}: ETL project to fetch data from several sources in proprietary formats into a unified data representation. Java,  Oracle PL/SQL, OpenAdaptor, Maven, Teamcity, Linux.
    \begin{itemize}%
        \item Improve feed processing performance to increase message volume with the same infrastructure.
        \item Design and perform application deployments on Linux servers.
        \item Analyse and improve the Software Development Life-Cycle (SDLC) for Source Control, Build Tools, Binary Control, Release Automation, Automated Testing and Continuous Integration.
    \end{itemize}
    \item \textbf{Legal Vehicle Database}: Track legal entity population for tax reporting purposes at Deutsche Bank. Java, GWT, Hibernate, Oracle.
    \begin{itemize}%
        \item Rewrite the user interface of an inherited project using Google Web Toolkit (GWT).
        \item Collaborate with software developers to deliver with adjusted deadline.
    \end{itemize}
    \item \textbf{Multichannel Platform}: Custom middleware that allows heterogeneous access to the bank mainframe resources of Bradesco Bank. Java, Eclipse Plug-in Development Environment.
    \begin{itemize}%
        \item Develop an Eclipse plugin which facilitate the location and communication of the processes that the platform of distribution of the channels exports or publishes.
    \end{itemize}
\end{itemize}
}

\cventry{2001--2005}{Java Developer}{Infoquip S.L.}{Valencia, Spain}{}{
Local company; 5 employees; Computer material store and custom software development.
\begin{itemize}%
    \item \textbf{Java Program Generator}: Java application generator to cut delivery times. Java, Swing, JDBC, MySQL, HTML, CSS, Linux.
    \begin{itemize}%
        \item Design and develop the engine for code generation.
        \item Develop a report generator, with viewer and printer.
        \item Design database to store application information and configuration.
    \end{itemize}
    \item \textbf{Sales point program} for furniture company. Java, Swing, JDBC, MySQL.
    \begin{itemize}%
        \item Sales program for interconnected stores.
        \item Take client requirements.
        \item Develop application using generator and adapt according to the client requirements.
    \end{itemize}
\end{itemize}
}

\cventry{1999--2000}{Technical School internship}{Infoquip S.L.}{Valencia, Spain}{}{
Local company; 5 employees; Computer material store and custom software development.\newline
\textbf{Internship}, 250 Hours.
\begin{itemize}%
    \item Learn Java programming language. Build and configure PCs and networks.
\end{itemize}
}


\section{Professional certification}
\cvitemwithcomment{Jun-2018}{Deep Learning and Neural Networks Specialization on Coursera}{}
\cvitemwithcomment{Sep-2016}{Machine Learning by Stanford University on Coursera}{}
\cvitemwithcomment{Apr-2013}{MongoDB for Java Developers}{M101J}
\cvitemwithcomment{Jul-2012}{Object Oriented Analysis and Design with UML}{}
\cvitemwithcomment{Mar-2011}{Oracle PL/SQL Developer Certified Associate}{OCA PL/SQL}
\cvitemwithcomment{Jan-2009}{Sun Certified Programmer for the Java Platform SE 6}{SCJP 6.0}


\section{Education}
\cventry{2004--2007}{Master of Computer Science}{Universidad Polit\'{e}cnica}{Valencia, Spain}{}{}
\cventry{2005}{ERASMUS grant}{University College of Engineering}{Odense, Denmark}{}{}
\cventry{2000--2004}{Bachelor of Computer Science}{Universidad Polit\'{e}cnica}{Valencia, Spain}{}{}
\cventry{1997--2000}{Technical School Management Information Systems}{I.E.S. El Caba\~{n}al}{Valencia, Spain}{}{}
\cventry{1996--1997}{Technical School Administrative Assistant}{I.F.P. La Marxadella}{Torrente, Spain}{}{}
\cventry{1995}{Primary School Graduated}{C.P. Ausi\`{a}s March}{Pica\~{n}a, Spain}{}{}


\section{Languages}
\cvitemwithcomment{English}{First Certificate English (FCE)}{Level B2 CEFR, Jul-2012}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{Catalan}{Native}{}

\section{Skills}
\cvitem{Languages}{Java (J2SE, J2EE), JavaScript, TypeScript, Python, Shell, scripting languages}
\cvitem{Web}{REST, HTML, CSS, JavaScript, Typescript, React, AngularJS, SAP UI5}
\cvitem{Frameworks}{Spring, Spring Boot, JPA, Hibernate}
\cvitem{Operating Systems}{Linux, Windows, Docker}
\cvitem{Databases}{Oracle SQL and PL/SQL, MySQL, SAP HANA}
\cvitem{Version Control}{Git, Subversion (SVN), CVS}
\cvitem{Testing}{Unit Testing, Integration Testing, JUnit, Mockito, Selenium, Karma, Mocha}
\cvitem{Methodology}{Agile software development, Scrum, Test Driven Development}
\cvitem{Servers}{Apache Tomcat, WebSphere, Jetty}
\cvitem{Build Tools}{Maven, Gradle, Ant, Webpack, Grunt, Gulp}
\cvitem{Continuous Integration}{Jenkins, Teamcity}

\end{document}

%% end of file `template.tex'.
